---
title: "Graphic Novels"
author: <span style="font-size:18px">Stephen Jones</span>
date: <span style="font-size:18px">March 16, 2019</span>
output:
  html_document:
    code_folding: hide
  pdf_document: default
---
<style type="text/css">
h1.title {
  color: DarkBlue;
  font-weight: bold;
}
h1 { /* Header 1 */
  color: DarkBlue;
  font-weight: bold;
}
h2 { /* Header 2 */
  color: DarkBlue;
  font-weight: bold;
}
h3 { /* Header 3 */
  color: DarkBlue;
  font-weight: bold;
}
h4 { /* Header 3 */
  color: DarkBlue;
  font-weight: bold;
}
pre { /* Code block - determines code spacing between lines */
  font-size: 12px;
  max-height: 300px;
  float: left;
  width: 100%;
  overflow-y: auto;
}
pre.r {
  max-height: none;
}
div.grey {
  background-color:#F3F2D8; 
  border-radius: 5px; 
  padding: 40px;
}
.btn {
    border-width: 0 0px 0px 0px;
    font-weight: normal;
    text-transform: ;
}
.btn-default {
    color: #2ecc71;
    background-color: #ffffff;
    border-color: #ffffff;
}
</style>
***  


##Observations - <i>Working with XML and JSON in R</i> {.tabset .tabset-fade}  

The tables and dataframes differ slightly; while creating the XML file I eliminated spaces in the column names and replaced with an underscore. The JSON file contained a heading "Graphic Novel" and different column/variable title "Name". Dates were also formatted differently. I tested an Access xml export function after creating the xml table manually as suggested (used here, above); the default settings produced complications but was informative.  


###XML {.tabset .tabset-fade .tabset-pills}  

Link: https://raw.githubusercontent.com/sigmasigmaiota/GraphicNovels/master/GraphicNovels.xml

#### Import

The packages `XML` and `RCurl` download the file from GitHub; then I convert to a list and bind into a dataframe. `kableExtra` displays the result.  

```{r warning=FALSE,message=FALSE,fig.align='center'}
library(XML)
library(RCurl)
library(kableExtra)

#set url, filename.
xmlurl<-"https://raw.githubusercontent.com/sigmasigmaiota/GraphicNovels/master/GraphicNovels.xml"

#RCurl.
xmlfile<-getURL(xmlurl)

#Parse the XML file.
xml.table <- xmlParse(xmlfile,useInternal=TRUE)
xml.table2<-xmlToList(xml.table)

#Convert to dataframe.
GN.xml<-do.call(rbind.data.frame, xml.table2)
rownames(GN.xml)<-NULL

kable(GN.xml)%>%
kable_styling()

```  

#### File  

The file, as it looks after download from GitHub.  

```{r message=FALSE, message=FALSE}

print(xml.table)

```

###JSON {.tabset .tabset-fade .tabset-pills}  

Link: https://raw.githubusercontent.com/sigmasigmaiota/GraphicNovels/master/GraphicNovels.json

####Import  

The package `jsonlite` is used to download and parse the JSON file.  

```{r warning=FALSE,message=FALSE,fig.align='center'}
library(jsonlite)

#set url, filename.
jsonurl<-"https://raw.githubusercontent.com/sigmasigmaiota/GraphicNovels/master/GraphicNovels.json"

#RCurl.
jsonfile<-getURL(jsonurl)

# Give the input file name to the function.
jsontable<- fromJSON(jsonfile)

#Unname the table to avoid column name changes.
GN.json<-as.data.frame(unname(jsontable))

kable(GN.json)%>%
kable_styling()

```  

#### File  

The file, as it looks after download from GitHub, before parsing.  

```{r message=FALSE, message=FALSE}

print(jsonfile)

```

###HTML {.tabset .tabset-fade .tabset-pills}  

Link: https://raw.githubusercontent.com/sigmasigmaiota/GraphicNovels/master/GraphicNovels.html

####Import  

The package `XML` is used to download and parse; `rlist` helps organize.  

```{r warning=FALSE,message=FALSE,fig.align='center'}

library(rlist)

htmlurl<-"https://raw.githubusercontent.com/sigmasigmaiota/GraphicNovels/master/GraphicNovels.html"

htmlfile<-getURL(htmlurl)

#Alternate command.
htmltable2<- readHTMLTable(htmlfile)
htmltable2<-list.clean(htmltable2,fun=is.null,recursive=FALSE)

#Unname the table to avoid column name changes.
GN.html<-as.data.frame(unname(htmltable2))

kable(GN.html)%>%
kable_styling()

```  

####File  

The file, as it looks after download from GitHub, before parsing.  

```{r message=FALSE, message=FALSE}

print(htmlfile)

```  


